Visual proteomics using whole-lamella 2D template matching

### 2022-02-23 manuscript.tex
Work on views and assembly [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/16c528a690632e78c5557a0164f560eef13aa854.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/16c528a690632e78c5557a0164f560eef13aa854/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1887731900

This manuscript
(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/fd67573aae85b96b8a70c12b88d9cb7dbe226559/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/fd67573aae85b96b8a70c12b88d9cb7dbe226559}{jojoelfe/deco\_lace\_template\_matching\_manuscript@fd67573}
on February 21, 2022.

>>>>

This manuscript
(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/16c528a690632e78c5557a0164f560eef13aa854/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/16c528a690632e78c5557a0164f560eef13aa854}{jojoelfe/deco\_lace\_template\_matching\_manuscript@16c528a}
on February 23, 2022.
